\documentclass[a4paper]{book}

\usepackage{afterpage}
\usepackage[hypcap=false]{caption}
\usepackage{cellspace}
\setlength\cellspacetoplimit{5pt}    % 设置单元格顶部最小间距
\setlength\cellspacebottomlimit{5pt} % 设置单元格底部最小间距
\usepackage{enumitem}	% 定制enumerate标号
\usepackage{geometry}
\geometry{%
	left=2cm,%
	right=2cm,%
	top=2cm,%
	bottom=2cm,%
	bindingoffset=0cm
}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,            %链接颜色
    linkcolor=blue,             %内部链接
    filecolor=magenta,          %本地文档
    urlcolor=cyan,              %网址链接
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
}
\usepackage[none]{hyphenat}	% 阻止长单词分在两行
\usepackage{longtable}
\usepackage{mathrsfs}	% 提供\mathscr字体
\usepackage[version=4]{mhchem}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{titlesec}

\RequirePackage[many]{tcolorbox}
\tcbset{
    boxed title style={colback=magenta},
	breakable,
	enhanced,
	sharp corners,
	attach boxed title to top left={yshift=-\tcboxedtitleheight,  yshifttext=-.75\baselineskip},
	boxed title style={boxsep=1pt,sharp corners},
    fonttitle=\bfseries\sffamily,
}

\definecolor{skyblue}{rgb}{0.54, 0.81, 0.94}

\newtcolorbox[auto counter, number within=chapter, number format=\arabic]{exercise}[1][]{
    title={Exercise~\thetcbcounter},
    colframe=skyblue,
    colback=skyblue!12!white,
    boxed title style={colback=skyblue},
    overlay unbroken and first={
        \node[below right,font=\small,color=skyblue,text width=.8\linewidth]
        at (title.north east) {#1};
    }
}

\newtcolorbox[auto counter, number within=chapter, number format=\arabic]{solution}[1][]{
%    top=2ex,
%    boxrule=0pt,
%    leftrule=1.4pt,
    title={Solution~\thetcbcounter},
    colframe=teal!60!green,
    colback=green!12!white,
    boxed title style={colback=teal!60!green},
    overlay unbroken and first={
        \node[below right,font=\small,color=red,text width=.8\linewidth]
        at (title.north east) {#1};
    }
}

\newtcolorbox{remark}[1][]{
    title={Remark},
    colframe=yellow!45!orange,
    colback=yellow!45!white,
    coltitle=white,
    boxed title style={colback=yellow!45!orange},
    overlay unbroken and first={
        \node[below right,font=\small,color=white,text width=.8\linewidth]
        at (title.north east) {#1};
    }
}

\newcommand{\AO}{{\rm AO}}
\newcommand{\Heff}{H^{\rm eff,\pi}}
\newcommand{\Hp}{H^\prime}
\newcommand{\Sp}{S^\prime}
\newcommand{\RRR}{{\rm R}^3}
\newcommand\Figref[1]{Fig \ref{#1}}
\newcommand\Tableref[1]{Table \ref{#1}}
\newcommand{\orb}[1]{{\rm #1}}
\newcommand{\orbs}{\orb{s}}
\newcommand{\orbp}{\orb{p}}
\newcommand{\orbd}{\orb{d}}
\newcommand{\orbf}{\orb{f}}

\allowdisplaybreaks

\titleformat{\chapter}[display]
  {\bfseries\Large}
  {\filright\MakeUppercase{\chaptertitlename} \Huge\thechapter}
  {1ex}
  {\titlerule\vspace{1ex}\filleft}
  [\vspace{1ex}\titlerule]

\begin{document}
	
	\setcounter{chapter}{6}
	
	\chapter{Irreducible Representations and Character Tables}
	
	% 7.1
	\begin{exercise}
		
		Given the characters $\chi$ of a reducible representation $\Gamma$ of the indicated point group $\mathscr{G}$ for the various classes of $\mathscr{G}$ in the order in which these classes appear in the character table, find the number of times irreducible representation occurs in $\Gamma$.
		\begin{enumerate}[label=(\alph*)]
		
		\item $\mathscr{C}_{\rm 2v}$ $\chi =$ 4, -2, 0, -2,
		
		\item $\mathscr{C}_{\rm 3h}$ $\chi =$ 4, 1, 1, 2, -1, -1,
		
		\item $\mathscr{D}_{\rm 4d}$ $\chi =$ 6, 0, -2, 0, -2, 0, 0,
		
		\item $\mathscr{O}_{\rm h}$ $\chi =$ 15, 0, -1, 1, 1, -3, 0, 5, -1 , 3.
		
		\end{enumerate}				
		
	\end{exercise}

	\begin{solution}
	
	There are two methods. I will show both for the first issue and treat the others in the same way.
		
	\begin{enumerate}[label=(\alph*)]
	
	\item Firstly, we show the character table of the point group $\mathscr{C}_{\rm 2v}$:
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{C}_{\rm 2v}$ point group.}\label{table:character_table_of_c2v}
	\begin{tabular}{c|cccc} \hline
		$\mathscr{C}_{\rm 2v}$ & $E$ & $C_2$ & $\sigma_{\rm v}(xz)$ & $\sigma_{\rm v}(yz)$ \\ \hline
		$A_1$	&	1	&	1	&	1	&	1	\\
		$A_2$	&	1	&	1	&	-1	&	-1	\\
		$B_1$	&	1	&	-1	&	1	&	-1	\\
		$B_2$	&	1	&	-1	&	-1	&	1	\\ \hline
	\end{tabular}
	\end{center}
	With (7-4.1), if we assume
	\begin{equation*}
		\Gamma^{\rm red} = a_1 \Gamma^{A_1} \oplus a_2 \Gamma^{A_2} \oplus b_1 \Gamma^{B_1} \oplus b_2 \Gamma^{B_2} ,
	\end{equation*}				
	where $a_1$, $a_2$, $b_1$ and $b_2$ are variables to be solved, then for class $\{E\}$,
	\begin{equation*}
		\chi^{\rm red}(E) = a_1 \chi^{A_1}(E) + a_2 \chi^{A_2}(E) + b_1 \chi^{B_1}(E) + b_2 \chi^{B_2}(E) ,
	\end{equation*}
	it will be
	\begin{equation*}
		1 \times a_1 + 1 \times a_2 + 1 \times b_1 + 1 \times b_2 = 4.
	\end{equation*}
	Similarly, for classes $\{C_2\}$, $\{ \sigma_{\rm v}(xz)\}$ and $\{ \sigma_{\rm v}(yz)\}$, we obtain
	\begin{align*}
		a_1 + a_2 - b_1 - b_2 &= -2 , \\
		a_1 - a_2 + b_1 - b_2 &= 0 , \\
		a_1 - a_2 - b_1 + b_2 &= -2 .
	\end{align*}
	Solve the group of linear equations in $Ax=b$ form, viz.
	\begin{equation*}
		\begin{pmatrix}
			1 & 1 & 1 & 1\\
			1 & 1 & -1 & -1 \\
			1 & -1 & 1 & -1 \\
			1 & -1 & -1 & 1
		\end{pmatrix}
		\begin{pmatrix}
			a_1 \\ a_2 \\ b_1 \\ b_2
		\end{pmatrix} =
		\begin{pmatrix}
			4 \\ -2 \\ 0 \\ -2
		\end{pmatrix},
	\end{equation*}
	it is easy to find
	\begin{equation*}
		a_1 = 0 , \quad a_2 = 1 , \quad b_1 = 2 , \quad b_2 = 1.
	\end{equation*}
	Thus,
	\begin{equation}
		\Gamma^{\rm red} = \Gamma^{A_2} \oplus 2 \Gamma^{B_1} \oplus \Gamma^{B_2} .
	\end{equation}
	
	Secondly, we can calculate reduction coefficients of the reducible representation $\Gamma^{\rm red}$ via (7-4.2). For instance, for the irreducible representation $A_1$,
	\[
		a_1 = \frac{1}{4} \left[ 1 \times 4 \times 1 + 1 \times (-2) \times 1 + 1 \times 0 \times 1 + 1 \times (-2) \times 1 \right] = \frac{1}{12} \times ( 4 - 2 + 0 - 2 ) = 0.
	\]
	In the same way, we can calculate others' reduction coefficients.
	\begin{align*}
		a_2 &= \frac{1}{4} ( 4 - 2 - 0 + 2 )= 1, \\
		b_1 &= \frac{1}{4} ( 4 + 2 + 0 + 2 )= 2, \\
		b_2 &= \frac{1}{4} ( 4 + 2 - 0 - 2 )= 1. 
	\end{align*}
	The final result is the same.

	\item We show the character table of the point group $\mathscr{C}_{\rm 3h}$:
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{C}_{\rm 3h}$ point group.}\label{table:character_table_of_c3h}
	\begin{tabular}{c|cccccc} \hline
		$\mathscr{C}_{\rm 3h}$ & $E$ & $C_3$ & $C^2_3$ & $\sigma_{\rm h}$ & $S_3$ & $S^5_3$ \\ \hline
		$A^\prime$	&	1	&	1	&	1	&	1	&	1	&	1	\\
		\multirow{2}*{$E^\prime$}	&	1	&	$\varepsilon$	&	$\varepsilon^*$	&	1	&	$\varepsilon$	&	$\varepsilon^*$	\\
					&	1	&	$\varepsilon^*$	&	$\varepsilon$	&	1	&	$\varepsilon^*$	&	$\varepsilon$	\\
		$A^{\prime\prime}$	&	1	&	1	&	1	&	-1	&	-1	&	-1	\\
		\multirow{2}*{$E^{\prime\prime}$}	&	1	&	$\varepsilon$	&	$\varepsilon^*$	&	-1	&	$-\varepsilon$	&	$-\varepsilon^*$	\\
					&	1	&	$\varepsilon^*$	&	$\varepsilon$	&	-1	&	$-\varepsilon^*$	&	$-\varepsilon$	\\ \hline
	\end{tabular}
	\end{center}
	The similar calculation process is omitted. However, using the first method, we will find that 
	\[
		a^\prime = 1, e^\prime = 1, e^\prime_* = 1 , a^{\prime\prime} = 1. 
	\]
	If the physical system of your interest has time-reversal symmetry, then the reduction coefficients of the $E$ and $E^*$ must be equal.
	
	The final result is
	\begin{equation}
		\Gamma^{\rm red} = \Gamma^{A^\prime} \oplus \Gamma^{E^\prime} \oplus \Gamma^{A^{\prime\prime}} .
	\end{equation}
	
	\item We show the character table of the point group $\mathscr{D}_{\rm 4d}$:
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{D}_{\rm 4d}$ point group.}\label{table:character_table_of_d4d}
	\begin{tabular}{c|ccccccc} \hline
		$\mathscr{D}_{\rm 4d}$ & $E$ & $2S_8$ & $2C_4$ & $2S^3_8$ & $C_2$ & $4C^\prime_2$ & $4 \sigma_{\rm d}$ \\ \hline
		$A_1$	&	1	&	1	&	1	&	1	&	1	&	1	&	1	\\
		$A_2$	&	1	&	1	&	1	&	1	&	1	&	-1	&	-1	\\
		$B_1$	&	1	&	-1	&	1	&	-1	&	1	&	1	&	-1	\\
		$B_2$	&	1	&	-1	&	1	&	-1	&	1	&	-1	&	1	\\
		$E_1$	&	2	& $\sqrt{2}$	& 0	& $-\sqrt{2}$ & -2 & 0 	&	0	\\
		$E_2$	&	2	& 	0	& 	-2	& 	0 	& 	2 	& 	0 	&	0	\\
		$E_3$	&	2	& $-\sqrt{2}$ & 0 & $\sqrt{2}$ & -2 & 0 	&	0	\\ \hline
	\end{tabular}
	\end{center}
	The similar calculation process is omitted. The final result is
	\begin{equation}
		\Gamma^{\rm red} = \Gamma^{E_1} \oplus \Gamma^{E_2} \oplus \Gamma^{E_3} .
	\end{equation}
	
	\item We show the character table of the point group $\mathscr{O}_{\rm h}$:
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{O}_{\rm h}$ point group.}\label{table:character_table_of_oh}
	\begin{tabular}{c|ccccccccccl@{\hspace{-8mm}}c} \hline
		$\mathscr{O}_{\rm h}$ & $E$ & $8C_3$ & $3C_2$ & $6C_4$ & $6C^\prime_2$ & $i$ & $8 S_6$ & $3 \sigma_{\rm h}$ & $6S_4$ & $6 \sigma_{\rm d}$ &	& \\ \hline
		$A_{1g}$	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	&	$x^2+y^2+z^2$	\\
		$A_{2g}$	&	1	&	1	&	1	&	-1	&	-1	&	1	&	1	&	1	&	-1	&	-1	&	&	\\
		$E_g$	&	2	&	-1	&	2	&	0	&	0	&	2	&	-1	&	2	&	0	&	0	&	&	($2z^2-x^2-y^2$, $x^2-y^2$)	\\
		$T_{1g}$ &	3	&	0	&	-1	&	1	&	-1	&	3	&	0	&	-1	&	1	&	-1	&	($R_x$, $R_y$, $R_z$)	&	\\
		$T_{2g}$ &	3	&	0	&	-1	&	-1	&	1	&	3	&	0	&	-1	&	-1	&	1	&	&	($xy$, $xz$, $yz$)		\\
		$A_{1u}$	&	1	&	1	&	1	&	1	&	1	&	-1	&	-1	&	-1	&	-1	&	-1	\\
		$A_{2u}$	&	1	&	1	&	1	&	-1	&	-1	&	-1	&	-1	&	-1	&	1	&	1	\\
		$E_g$	&	2	&	-1	&	2	&	0	&	0	&	-2	&	1	&	-2	&	0	&	0	\\
		$T_{1u}$	 & 	3	&	0	&	-1	&	1	&	-1	&	-3	&	0	&	1	&	-1	&	1	&	($x$, $y$, $z$)\\
		$T_{2u}$ &	3	&	0	&	-1	&	-1	&	1	&	-3	&	0	&	1	&	1	&	-1	\\ \hline
	\end{tabular}
	\end{center}

	The similar calculation process is omitted. The final result is
	\begin{equation}
		\Gamma^{\rm red} = \Gamma^{A_{1g}} \oplus \Gamma^{E_g} \oplus \Gamma^{T_{2g}} \oplus 2 \Gamma^{T_{1u}} \oplus \Gamma^{T_{2u}} .
	\end{equation}

	\end{enumerate}

	\end{solution}
	
	\begin{remark}
	
	I think that the solution of the system of linear equations is better than the application of reduction formula, viz., (7-4.2) in the textbook. There are two aspects.
	
	\begin{itemize}
	
	\item Algorithm Efficiency: In group representation theory, assume the number of (conjugate) classes of a group is $n$ (which is also equal to the number of irreducible representations). We analyse the calculation complexity of these two methods firstly.
		\begin{itemize}
		
		\item Reduction formula: You need to calculate $\frac{1}{g}\sum g_i \chi^{\rm red}(g)\chi^i(g)$ once for each irreducible representation $\Gamma^i$. For all irreducible representations, the total complexity is approximately $O(n^2)$.
		
		\item Solution of the system of linear equations: Essentially, it solves $Ax = b$, where $A$ is the feature table matrix ($n \times n$). Using the Gauss-Jordan method or LU decomposition, the complexity is $O(n^3)$.
		
		\end{itemize}
	   Theoretically, $O(n^2)$ is better than $O(n^3)$. However, in practice, the $n$ of a point group is extremely small (usually $< 20$), and $20^3$ can be completed in microseconds for a modern computer. On the contrary, because the solution of the system of linear equations can solve for all coefficients at once, the engineering overhead is actually smaller when calling mature linear algebra libraries (such as \verb!numpy.linalg.solve! in Python language).
	   
	\item Engineering Implementation: When writing scripts, the solution of the system of linear equations has several significant engineering advantages.
	
		\begin{itemize}
		
		\item Code conciseness: There is no need to write complex loops for weighted summation; a single line of \verb!numpy.linalg.solve(A, b)! does the trick.
		
		\item Robustness check: The solved coefficients $a_i$ must be non-negative integers. In programming, you can use this for validation: if the solution has components like 0.333333 or -1, the program can immediately report an error, reminding you that at least one of $A$ and $b$ is incorrect.
		
		\item Matrix reuse: If multiple different representations of the same point group (such as vibration representation, rotation representation, orbital representation) are decomposed, the matrix $A$ remains unchanged. You can invert or decompose $A$ beforehand, and the subsequent reduction becomes pure matrix multiplication, instantly boosting efficiency.
		
		\end{itemize}
	
	\end{itemize}
		
	\end{remark}

	% 7.2
	\begin{exercise}
	
	Consider the four functions of Problem 5.2 which form a basis for a reducible representation $\Gamma$ of $\mathscr{D}_4$. Using projection operators find the orthonormal basis functions which reduce $\Gamma$. Assume $(f_i, f_j) = \delta_{ij}$.	
		
	\end{exercise}

	\begin{solution}
	
	We show the character table of the point group $\mathscr{D}_{\rm 4}$:
	\begin{center}
	\setlength{\abovecaptionskip}{0em}
	\captionof{table}{The character table for the $\mathscr{D}_{\rm 4}$ point group.}\label{table:character_table_of_d4}
	\begin{tabular}{c|ccccccc}\hline
$\mathscr{D}_{\rm 4}$ & $E$ & $2C_4$ &	$C_2$	& $2C^\prime_2$ & $2C^{\prime\prime}_2$ & & \\ \hline
		$A_1$	&	1	&	1	&	1	&	1	&	1	&	&	$x^2+y^2$; $z^2$ \\
		$A_2$	&	1	&	1	&	1	&	-1	&	-1	&	$z$; $R_z$	&	\\
		$B_1$	&	1	&	-1	&	1	&	1	&	-1	&	&	$x^2-y^2$	\\
		$B_2$	&	1	&	-1	&	1	&	-1	&	1	&	&	$xy$		\\
		$E$ 		&	2	&	0	&	-2	&	0	&	0	&	($x$, $y$); ($R_x$, $R_y$)	&	($xz$, $yz$)		\\ \hline
	\end{tabular}
	\end{center}
	
	From the matrix representation of Problem 5.2, we obtain the character for the reducible representation $\Gamma^{\rm red}$ of the $\mathscr{D}_4$ point group:
	\begin{center}
	\captionof{table}{Characters for the $\Gamma^{\ce{CN}}$ of the $\mathscr{D}_4$ point group.}\label{table:characters_for_d4}
	\begin{tabular}{c|ccccc}\hline
		$\mathscr{D}_4$ & $E$ & $2C_4$ &	$C_2$	& $2C^\prime_2$	&	$2C^{\prime\prime}_2$ 	\\ \hline
		$\chi^{\rm red}(C_i)$&	4	&	0	&	0	&	0	&	-2  \\ \hline
	\end{tabular}
	\end{center}
	
	Immediately, we obtain
	\begin{equation}
		\Gamma^{\rm red} = \Gamma^{A_2} \oplus \Gamma^{B_1} \oplus \Gamma^E .
	\end{equation}
	
	Then, we show the effects of the transformation operators $\boldsymbol{O}_R$ for the symmetry operation $R$ of the point group $\mathscr{D}_4$ on four functions $f_1$, $f_2$, $f_3$, and $f_4$:
	\begin{center}
	\captionof{table}{Effects of the transformation operators $\boldsymbol{O}_R$ for the symmetry operation $R$ of the point group $\mathscr{D}_4$ on four functions $f_1$, $f_2$, $f_3$, and $f_4$.}
	\begin{tabular}{c|cccccccc}\hline
	$R =$ & $E$ & $C_4$ & $C^3_4$ & $C_2$ & $C^\prime_{2a}$ & $C^\prime_{2b}$ & $C^{\prime\prime}_{2a}$ & $C^{\prime\prime}_{2b}$ \\ \hline 
	$f_1$ & $f_1$ & $f_2$ & $f_4$ & $f_3$ & $-f_4$ & $-f_2$ & $-f_1$ & $-f_3$ \\
	$f_2$ & $f_2$ & $f_3$ & $f_1$ & $f_4$ & $-f_3$ & $-f_1$ & $-f_4$ & $-f_2$ \\
	$f_3$ & $f_3$ & $f_4$ & $f_2$ & $f_1$ & $-f_2$ & $-f_4$ & $-f_3$ & $-f_1$ \\
	$f_4$ & $f_4$ & $f_1$ & $f_3$ & $f_2$ & $-f_1$ & $-f_3$ & $-f_2$ & $-f_4$ \\ \hline
	\end{tabular}
	\end{center}
	Thus, using eqn (7-6.6), the only basis function in $\Gamma^{A_2}$ is
	\begin{align*}
		f^{A_2} &= \left[ \sum_R \chi^{A_2}(R)^* \boldsymbol{O}_R \right] f_1 \\
				&= \left[ \chi^{A_2}(E)^* \boldsymbol{O}_E + \chi^{A_2}(C_4)^* \boldsymbol{O}_{C_4} + \chi^{A_2}(C_2)^* \boldsymbol{O}_{C_2} + \chi^{A_2}(C^3_4)^* \boldsymbol{O}_{C^3_4} \right. \\
				&\hspace{4em} \left. + \chi^{A_2}(C^\prime_{2a})^* \boldsymbol{O}_{C^\prime_{2a}} + \chi^{A_2}(C^\prime_{2b})^* \boldsymbol{O}_{C^\prime_{2b}} + \chi^{A_2}(C^{\prime\prime}_{2a})^* \boldsymbol{O}_{C^{\prime\prime}_{2a}} + \chi^{A_2}(C^{\prime\prime}_{2b})^* \boldsymbol{O}_{C^{\prime\prime}_{2b}} \right]  f_1 \\
				&= \left( \boldsymbol{O}_E + \boldsymbol{O}_{C_4} + \boldsymbol{O}_{C_2} + \boldsymbol{O}_{C^3_4} - \boldsymbol{O}_{C^\prime_{2a}} - \boldsymbol{O}_{C^\prime_{2b}} - \boldsymbol{O}_{C^{\prime\prime}_{2a}} - \boldsymbol{O}_{C^{\prime\prime}_{2b}} \right) f_1 \\
				&= \boldsymbol{O}_E f_1 + \boldsymbol{O}_{C_4} f_1 + \boldsymbol{O}_{C_2} f_1 + \boldsymbol{O}_{C^3_4} f_1 - \boldsymbol{O}_{C^\prime_{2a}} f_1 - \boldsymbol{O}_{C^\prime_{2b}} f_1 - \boldsymbol{O}_{C^{\prime\prime}_{2a}} f_1 - \boldsymbol{O}_{C^{\prime\prime}_{2b}} f_1 \\
				&= f_1 + f_2 + f_3 + f_4 - (-f_4) - (-f_2) - (-f_1) - (-f_3) \\
				&= 2 ( f_1 + f_2 + f_3 + f_4 ) .
	\end{align*}
	The inner product of $\Gamma^{A_2}$ is
	\begin{equation*}
		( f^{A_2} | f^{A_2} ) = \left( 2 \sum^4_{i=1} f_i \middle| 2 \sum^4_{j=1} f_j \right) = 4 \sum^4_{i=1} \sum^4_{j=1} ( f_i | f_j ) = 4 \sum^4_{i=1} \sum^4_{j=1}  \delta_{ij} = 4 \sum^4_{i=1} 1 = 4 \times 4 = 16 .
	\end{equation*}
	Therefore, the normalized basis function $f^{A_2}$ is
	\begin{equation*}
		f^{A_2 \prime} = \frac{1}{ \sqrt{ ( f^{A_2} | f^{A_2} ) } } f^{A_2} = \frac{1}{4} \times 2 ( f_1 + f_2 + f_3 + f_4 ) = \frac{1}{2} ( f_1 + f_2 + f_3 + f_4 ) .
	\end{equation*}
	
	Similarly, we obtain
	\begin{equation*}
		f^{B_1 \prime} = \frac{1}{ \sqrt{ ( f^{B_1} | f^{B_1} ) } } f^{B_1} = \frac{1}{4} \times 2 ( f_1 - f_2 + f_3 - f_4 ) = \frac{1}{2} ( f_1 - f_2 + f_3 - f_4 ) .
	\end{equation*}
	
	For the two-dimentional irreducible representation $\Gamma^E$, we have
	\begin{align*}
		f^E_1 &= 2 \boldsymbol{O}_E f_1 - 2 \boldsymbol{O}_{C_2} f_1 = 2 f_1 - 2 f_3 = 2 ( f_1 - f_3 ) , \\
		f^E_2 &= 2 \boldsymbol{O}_E f_2 - 2 \boldsymbol{O}_{C_2} f_4 = 2 f_2 - 2 f_4 = 2 ( f_2 - f_4 ) .
	\end{align*}
	In fact, $f^E_1$ has been perpendicular to $f^{E_2}$:
	\begin{align*}
		( f^E_1 | f^E_2 ) &= ( 2 (f_1 - f_3) | 2(f_2 - f_4) ) = 4 \left[ ( f_1 | f_2 ) - ( f_1 | f_4 ) - ( f_3 | f_2 ) + ( f_3 | f_4 ) \right] = 4 \times 0 = 0 , \\
		( f^E_2 | f^E_1 ) &= ( 2 (f_2 - f_4) | 2(f_1 - f_3) ) = 4 \left[ ( f_2 | f_1 ) - ( f_2 | f_3 ) - ( f_4 | f_1 ) + ( f_4 | f_3 ) \right] = 4 \times 0 = 0 .		
	\end{align*}
	Thus we just normalize $f^{E_1}$ and $f^{E_2}$:
	\begin{align*}
		f^{E \prime}_1 = \frac{1}{ \sqrt{ ( f^E_1 | f^E_1 ) } } f^E_1 = \frac{1}{2\sqrt{2}} \times 2 ( f_1 - f_3 ) = \frac{1}{ \sqrt{2} } ( f_1 - f_3 ) , \\
		f^{E \prime}_2 = \frac{1}{ \sqrt{ ( f^E_2 | f^E_2 ) } } f^E_2 = \frac{1}{2\sqrt{2}} \times 2 ( f_2 - f_4 ) = \frac{1}{ \sqrt{2} } ( f_2 - f_4 ) .
	\end{align*}
	
	Summing these contributions, we get the four orthonormal basis functions which reduce $\Gamma$:
	\begin{align}
		f^{A_2 \prime} &= \frac{1}{2} ( f_1 + f_2 + f_3 + f_4 ) , \\
		f^{B_1 \prime} &= \frac{1}{2} ( f_1 - f_2 + f_3 - f_4 ) , \\
		f^{E \prime}_1 &= \frac{1}{ \sqrt{2} } ( f_1 - f_3 ) , \\
		f^{E \prime}_2 &= \frac{1}{ \sqrt{2} } ( f_2 - f_4 ) .
	\end{align}
	\end{solution}
	
	\begin{remark}
	
	For multi-dimensional irreducible representations, the projection operators typically generate a set of basis functions that are linearly independent but not necessarily orthogonal. Various orthogonalization methods can be employed; a robust approach is the symmetric (L{\"o}wdin) orthogonalization. In this approach, after obtaining $n_\nu$ basis functions, $f^\nu_1$, $f^\nu_2$, $\ldots$, $f^\nu_{n_\nu}$, we first construct their overlap matrix $S^\nu$:
		\begin{equation}
			S^\nu_{ij} \equiv (\langle f^\nu_i | f^\nu_j \rangle)_{n_\nu \times n_\nu} = \begin{pmatrix}
			\langle f^\nu_1 | f^\nu_1 \rangle & \langle f^\nu_1 | f^\nu_2 \rangle & \ldots & \langle f^\nu_1 | f^\nu_{n_\nu} \rangle \\
			\langle f^\nu_2 | f^\nu_1 \rangle & \langle f^\nu_2 | f^\nu_2 \rangle & \ldots & \langle f^\nu_2 | f^\nu_{n_\nu} \rangle \\
			\vdots & \vdots & \ddots & \vdots \\ 
			\langle f^\nu_{n_\nu} | f^\nu_1 \rangle & \langle f^\nu_{n_\nu} | f^\nu_2 \rangle & \ldots & \langle f^\nu_{n_\nu} | f^\nu_{n_\nu} \rangle\end{pmatrix}
			\end{equation}
		Then, the orthonormal basis functions $\{f^{\nu\prime}_i\}$ are generated via:
		\begin{equation}
			f^{\nu\prime}_i = \sum_{j=1}^{n_\nu} f^\nu_j [(S^\nu)^{-1/2}]_{ji}.
		\end{equation}
		
		Compared to the Schmidt orthogonalization, there are two merits for symmetric orthogonalization.
		\begin{itemize}
		
		\item Minimum Deviation (Least-Squares Property): It can be mathematically proven that the symmetric orthogonalization minimizes the sum of squared differences between the orthonormal basis $\{f'_i\}$ and the original basis $\{f_i\}$. Consequently, it maximizes the preservation of the physical characteristics and spatial symmetry of the original basis functions.
		
		\item Equivalence (Order Independence): Unlike the Gram-Schmidt process shown in the A.6-2 section in the textbook, which is inherently sequential and dependent on the ordering of the basis set, the symmetric method treats all original basis functions equivalently (i.e., it is a democratic orthogonalization).
		
		\end{itemize}
		
	Thus, this method is particularly well-suited for constructing Symmetry-Adapted Linear Combinations (SALCs) based on these two advantages.
	
	\end{remark}

	% 7.3
	\begin{exercise}
	
	Show that the characters of $\mathscr{C}_{\rm 4v}$ obey the orthogonality rules of eqns (7.3-5) and (A.7-3.10).
	
	\end{exercise}
	
	\begin{solution}
	
	The direct validity of eqns (7.3-5) and (A.7-3.10) is boring and tedious. Therefore, I have designed a Python script to finish this Problem. This script lies on \verb!../scripts/chapter_07! and is called \verb!check_two_equations.py!. More than the $\mathscr{C}_{\rm 4v}$ point group, these equations on the $\mathscr{T}_{\rm d}$ point group are also checked in this script as another example. The character tables for the $\mathscr{C}_{\rm 4v}$ and $\mathscr{T}_{\rm d}$ are shown in \Tableref{table:character_table_of_c4v} and \Tableref{table:character_table_of_td}, respectively.
	
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{C}_{\rm 4v}$ point group.}\label{table:character_table_of_c4v}
	\begin{tabular}{c|ccccc} \hline
		$\mathscr{C}_{\rm 4v}$ & $E$ & $2C_4$ & $C_2$ & $2\sigma_{\rm v}$ & $\sigma_{\rm d}$ \\ \hline
		$A_1$	&	1	&	1	&	1	&	1	&	1	\\
		$A_2$	&	1	&	1	&	1	&	-1	&	-1	\\
		$B_1$	&	1	&	-1	&	1	&	1	&	-1	\\
		$B_2$	&	1	&	-1	&	1	&	-1	&	1	\\
		$E$		&	2	&	0	&	-2	&	0	&	0  	\\ \hline
	\end{tabular}
	\end{center}	
	
	\end{solution}
	
	% 7.4
	\begin{exercise}
		
	How many times does each irreducible representation of the $\mathscr{C}_{\rm 2v}$ point group occur in the nine-dimentional representation found in Problem 5.3?
		
	\end{exercise}
	
	\begin{solution}
	
		The character table of $\mathscr{C}_{\rm 2v}$ is illustrated in \Tableref{table:character_table_of_c2v}. Using the solution of the system of linear equations, we immediately obtain
		\begin{equation}
			\Gamma^{\rm red} = 3 \Gamma^{A_1} \oplus \Gamma^{A_2} \oplus 2 \Gamma^{B_1} \oplus 3 \Gamma^{B_2} .
		\end{equation}
	
	\end{solution}
	
	% 7.5
	\begin{exercise}
		
	Consider the group whose group table is
	\begin{center}
	\begin{tabular}{c|cccc}\hline
			&	$E$	&	$A$	&	$B$	&	$C$	\\ \hline
		$E$	&	$E$	&	$A$	&	$B$	&	$C$	\\
		$A$	&	$A$	&	$C$	&	$E$	&	$B$	\\
		$B$	&	$B$	&	$E$	&	$C$	&	$A$	\\
		$C$	&	$C$	&	$B$	&	$A$	&	$E$	\\ \hline
	\end{tabular}
	\end{center}
	write out the matrices and characters for the regular representation of this group.

	\end{exercise}
	
	\begin{solution}
	
	Firstly, we need to rearrange the group multiplication table to ensure that the identity element E is always on its diagonal:
	\begin{center}
	\begin{tabular}{c|cccc}\hline
					&	$E$	&	$A$	&	$B$	&	$C$	\\ \hline
		$E^{-1}=E$	&	$E$	&	$A$	&	$B$	&	$C$	\\
		$A^{-1}=B$	&	$B$	&	$E$	&	$C$	&	$A$	\\
		$B^{-1}=A$	&	$A$	&	$C$	&	$E$	&	$B$	\\
		$C^{-1}=C$	&	$C$	&	$B$	&	$A$	&	$E$	\\ \hline
	\end{tabular}
	\end{center}
	
	According to its definition, it is easy to construct the regular representation of this group, summing as follows.
	\begin{center}
	\captionof{table}{The regular representation of the group in current Problem. The order of the basis is $E$, $A$, $B$ and $C$.}
	\begin{tabular}{c|ScScScSc}\hline
		$R=$ 	& $E$	&	$A$		&	$B$	&	$C$	\\ \hline
		$D(R)$	& $\begin{pmatrix}
			1 & 0 & 0 & 0 \\
			0 & 1 & 0 & 0 \\
			0 & 0 & 1 & 0 \\
			0 & 0 & 0 & 1
		\end{pmatrix}$ & $\begin{pmatrix}
			0 & 1 & 0 & 0 \\
			0 & 0 & 0 & 1 \\
			1 & 0 & 0 & 0 \\
			0 & 0 & 1 & 0
		\end{pmatrix}$ & $\begin{pmatrix}
			0 & 0 & 1 & 0 \\
			1 & 0 & 0 & 0 \\
			0 & 0 & 0 & 1 \\
			0 & 1 & 0 & 0
		\end{pmatrix}$ & $\begin{pmatrix}
			0 & 0 & 0 & 1 \\
			0 & 0 & 1 & 0 \\
			0 & 1 & 0 & 0 \\
			1 & 0 & 0 & 0
		\end{pmatrix}$ \\ \hline
	\end{tabular}
	\end{center}
	
	At last, we know the characters for the regular representation of this group.
	\begin{center}
	\captionof{table}{The characters for the regular representation of this group.}
	\begin{tabular}{c|cccc}\hline
		 			& $E$	&	$A$	&	$B$	&	$C$	\\ \hline
		$\chi^{\rm reg}(R)$	&	4	&	0	&	0	&	0	\\ \hline
	\end{tabular}
	\end{center}
	
	\end{solution}
	
	% 7.6
	\begin{exercise}
		
	Determine the irreducible representation to which the following real orbitals belong for the indicated point group:
	\begin{enumerate}[label=(\alph*)]
	
	\item $\orbp_1$, $\orbp_2$, $\orbp_3$ in $\mathscr{D}_4$ and $\mathscr{D}_{\rm 2h}$ ,
	
	\item $\orbd_1$, $\orbd_2$, $\orbd_3$, $\orbd_4$, $\orbd_5$ in $\mathscr{O}_{\rm h}$,
	
	\item $\orbd_1$, $\orbd_2$, $\orbd_3$, $\orbd_4$, $\orbd_5$ in $\mathscr{D}_{\rm 3h}$,
	
	\item $\orbd_1$, $\orbd_2$, $\orbd_3$, $\orbd_4$, $\orbd_5$ in $\mathscr{T}_{\rm d}$.
	
	\end{enumerate}	
		
	\end{exercise}
	
	\begin{solution}
	
	If readers only care about the final result, it will be enough to check the character tables. Here, I will show the solution processes, taking only the Problem 7.6 (a) as an instance. And then list all results, omitting others' solution processes.
	
	\begin{enumerate}[label=(\alph*)]

	\item The character table of the $\mathscr{D}_{\rm 4}$ and $\mathscr{D}_{\rm 2h}$ can be seen in \Tableref{table:character_table_of_d4} and \Tableref{table:character_table_of_d2h}, respectively.
		\begin{center}
		\captionof{table}{The character table for the $\mathscr{D}_{\rm 2h}$ point group.} \label{table:character_table_of_d2h}
		\begin{tabular}{c|cccccccccc}\hline
	$\mathscr{D}_{\rm 2h}$ & $E$ & $C_2(z)$ & $C_2(y)$ & $C_2(x)$ & $i$ & $\sigma(xy)$ & $\sigma(xz)$ & $\sigma(yz)$	&	&	 \\ \hline
			$A_g$	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	1	&	&	$x^2$; $y^2$; $z^2$	\\
			$B_{1g}$	&	1	&	1	&	-1	&	-1	&	1	&	1	&	-1	&	-1	&	$R_z$	&	$xy$		\\
			$B_{2g}$	&	1	&	-1	&	1	&	-1	&	1	&	-1	&	1	&	-1	&	$R_y$	&	$xz$		\\
			$B_{3g}$	&	1	&	-1	&	-1	&	1	&	1	&	-1	&	-1	&	1	&	$R_x$	&	$yz$	\\
			$A_u$	&	1	&	1	&	1	&	1	&	-1	&	-1	&	-1	&	-1	&	&	\\
			$B_{1u}$	&	1	&	1	&	-1	&	-1	&	-1	&	-1	&	1	&	1	&	$z$	&	\\
			$B_{2u}$	&	1	&	-1	&	1	&	-1	&	-1	&	1	&	-1	&	1	&	$y$	&	\\
			$B_{3u}$	&	1	&	-1	&	-1	&	1	&	-1	&	1	&	1	&	-1	&	$x$	&	\\ \hline
		\end{tabular}
		\end{center}
		
		The characters for the reducible representation $\Gamma^{\rm red}$ of the $\mathscr{D}_4$ is:
		\begin{center}
		\captionof{table}{Characters for the $\Gamma^{\rm red}$ of the $\mathscr{D}_4$ point group.}
		\begin{tabular}{c|ccccc}\hline
			$\mathscr{D}_4$ & $E$ & $2C_4$ &	$C_2$	& $2C^\prime_2$	&	$2C^{\prime\prime}_2$ 	\\ \hline
			$\chi^{\rm red}(C_i)$&	3	&	1	&	-1	&	-1	&	-1  \\ \hline
		\end{tabular}
		\end{center}
		And then we decompose the reducible representation:
		\begin{equation}
			\Gamma^{\rm red} = \Gamma^{A_2} \oplus \Gamma^E .
		\end{equation}
		Then, we test the effects of the transformation operators $\boldsymbol{O}_R$ for the symmetry operation $R$ of the point group $\mathscr{D}_4$ on two functions $\orbp_1$, and $\orbp_3$. At this time, $\orbp_1$ and $\orbp_2$ are equivalent in chemists' view and thus we do not test $\orbp_2$.
		\begin{center}
		\captionof{table}{Effects of the transformation operators $\boldsymbol{O}_R$ for the symmetry operation $R$ of the point group $\mathscr{D}_4$ on four functions $\orbp_1$, and $\orbp_3$.}
		\begin{tabular}{c|cccccccc}\hline
		$R =$ & $E$ & $C_4$ & $C^3_4$ & $C_2$ & $C^\prime_{2a}$ & $C^\prime_{2b}$ & $C^{\prime\prime}_{2a}$ & $C^{\prime\prime}_{2b}$ \\ \hline 
		$\orbp_1$ & $\orbp_1$ & $-\orbp_2$ & $-\orbp_1$ & $\orbp_2$ & $\orbp_1$ & $-\orbp_1$ & $\orbp_2$ & $-\orbp_2$ \\
		$\orbp_3$ & $\orbp_3$ & $\orbp_3$ & $\orbp_3$ & $\orbp_3$ & $-\orbp_3$ & $-\orbp_3$ & $-\orbp_3$ & $-\orbp_3$  \\ \hline
		\end{tabular}
		\end{center}
		
		Similar to Problem 7.2, we check whether $\orbp_1$ is a basis function for $\Gamma^{A_2}$:
		\begin{align*}
		&\hspace{1.3em} \left[ \sum_R \chi^{A_2}(R)^* \boldsymbol{O}_R \right] \orbp_1 \\
		&= \left[ \chi^{A_2}(E)^* \boldsymbol{O}_E + \chi^{A_2}(C_4)^* \boldsymbol{O}_{C_4} + \chi^{A_2}(C_2)^* \boldsymbol{O}_{C_2} + \chi^{A_2}(C^3_4)^* \boldsymbol{O}_{C^3_4} \right. \\
		&\hspace{4em} \left. + \chi^{A_2}(C^\prime_{2a})^* \boldsymbol{O}_{C^\prime_{2a}} + \chi^{A_2}(C^\prime_{2b})^* \boldsymbol{O}_{C^\prime_{2b}} + \chi^{A_2}(C^{\prime\prime}_{2a})^* \boldsymbol{O}_{C^{\prime\prime}_{2a}} + \chi^{A_2}(C^{\prime\prime}_{2b})^* \boldsymbol{O}_{C^{\prime\prime}_{2b}} \right]  \orbp_1 \\
		&= \left( \boldsymbol{O}_E + \boldsymbol{O}_{C_4} + \boldsymbol{O}_{C_2} + \boldsymbol{O}_{C^3_4} - \boldsymbol{O}_{C^\prime_{2a}} - \boldsymbol{O}_{C^\prime_{2b}} - \boldsymbol{O}_{C^{\prime\prime}_{2a}} - \boldsymbol{O}_{C^{\prime\prime}_{2b}} \right) \orbp_1 \\
		&= \boldsymbol{O}_E \orbp_1 + \boldsymbol{O}_{C_4} \orbp_1 + \boldsymbol{O}_{C_2} \orbp_1 + \boldsymbol{O}_{C^3_4} \orbp_1 - \boldsymbol{O}_{C^\prime_{2a}} \orbp_1 - \boldsymbol{O}_{C^\prime_{2b}} \orbp_1 - \boldsymbol{O}_{C^{\prime\prime}_{2a}} \orbp_1 - \boldsymbol{O}_{C^{\prime\prime}_{2b}} \orbp_1 \\
		&= \orbp_1 - \orbp_2 - \orbp_1 + \orbp_2 - \orbp_1 - (-\orbp_1) - \orbp_2 - (-\orbp_2) = 0 .
		\end{align*}
		It is clear that $\orbp_1$ is not a basis function of $\Gamma^{A_2}$. In the same way, we can find 
		\begin{equation*}
			\left[ \sum_R \chi^{A_2}(R)^* \boldsymbol{O}_R \right] \orbp_3 = 8 \orbp_3 .
		\end{equation*}
		Thus, we ensure that $\orbp_3$ belongs to $\Gamma^{A_2}$ for the $\mathscr{D}_4$ point group, and the $\orbp_1$ and $\orbp_2$ should belong to the only other $\Gamma^E$ for the $\mathscr{D}_4$ point group.
		
		In the same way, we calculate the characters for the reducible representation $\Gamma^{\rm red}$ of the $\mathscr{D}_{\rm 2h}$:
		\begin{center}
		\captionof{table}{Characters for the $\Gamma^{\rm red}$ of the $\mathscr{D}_{\rm 2h}$ point group.}
		\begin{tabular}{c|cccccccc}\hline
			$\mathscr{D}_{\rm 2h}$ & $E$ & $C_2(z)$ & $C_2(y)$ & $C_2(x)$ & $i$ & $\sigma(xy)$ & $\sigma(xz)$ & $\sigma(yz)$ \\ \hline
			$\chi^{\rm red}(C_i)$&	3	&	-1	&	-1	&	-1	&	-3	&	1	&	1	&	1  \\ \hline
		\end{tabular}
		\end{center}
		And then we decompose the reducible representation:
		\begin{equation}
			\Gamma^{\rm red} = \Gamma^{B_{1u}} \oplus \Gamma^{B_{2u}} \oplus \Gamma^{B_{3u}} .
		\end{equation}
		In the same way, we ensure that $\orbp_1$, $\orbp_2$ and $\orbp_3$ belongs to  $\Gamma^{B_{3u}}$, $\Gamma^{B_{2u}}$, and $\Gamma^{B_{1u}}$ for the $\mathscr{D}_{\rm 2h}$, respectively.
		
	\item The character table of the $\mathscr{O}_{\rm h}$ can be seen in \Tableref{table:character_table_of_oh}. From this table, we ensure that both $\orbd_1$ and $\orbd_5$ belong to $\Gamma^{E_g}$, and all $\orbd_2$, $\orbd_3$ and $\orbd_4$ belong to $\Gamma^{T_{2g}}$.
	
	\item The character table of the $\mathscr{D}_{\rm 3h}$ can be seen in \Tableref{table:character_table_of_d3h}. From this table, we ensure that $\orbd_5$ belongs to the $\Gamma^{A^\prime_1}$, both $\orbd_1$ and $\orbd_2$ belong to $\Gamma^{E^\prime}$, and both $\orbd_3$ and $\orbd_4$ belong to $\Gamma^{E^{\prime\prime}}$.
	
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{D}_{\rm 3h}$ point group.} \label{table:character_table_of_d3h}
	\begin{tabular}{c|cccccccc}\hline
$\mathscr{D}_{\rm 3h}$ & $E$ & $2C_3$ & $3C_2$ &	$\sigma_{\rm h}$	& $2S_3$ & $3\sigma_{\rm v}$	&	& \\ \hline
		$A^\prime_1$	&	1	&	1	&	1	&	1	&	1	&	1	&	&$x^2+y^2$; $z^2$	\\
		$A^\prime_2$	&	1	&	1	&	-1	&	1	&	1	&	-1	&	$R_z$	&	\\
		$E^\prime$	&	2	&	-1	&	0	&	2	&	-1	&	0	& ($x$, $y$)	&	($x^2-y^2$, $xy$)\\
		$A^{\prime\prime}_1$	&	1	&	1	&	1	&	-1	&	-1	&	-1	&	&	\\
		$A^{\prime\prime}_2$	&	1	&	1	&	-1	&	-1	&	-1	&	1	&	$z$	&	\\
		$E^{\prime\prime}$	&	2	&	-1	&	0	&	-2	&	1	&	0	&	($R_x$, $R_y$)	&	($xz$, $yz$)	\\ \hline
	\end{tabular}
	\end{center}
	
	\item The character table of the $\mathscr{T}_{\rm d}$ can be seen in \Tableref{table:character_table_of_td}. From this table, we ensure that both $\orbd_1$ and $\orbd_5$ belong to $\Gamma^E$, and all $\orbd_2$, $\orbd_3$ and $\orbd_4$ belong to $\Gamma^{T_2}$.
	
	\begin{center}
	\captionof{table}{The character table for the $\mathscr{T}_{\rm d}$ point group.} \label{table:character_table_of_td}
	\begin{tabular}{c|ccccccc}\hline
$\mathscr{T}_{\rm d}$ & $E$ & $8C_3$ & $3C_2$ & $6S_4$ & $6\sigma_d$	&	& \\ \hline
		$A_1$	&	1	&	1	&	1	&	1	&	1	&	&	$x^2+y^2+z^2$\\
		$A_2$	&	1	&	1	&	1	&	-1	&	-1	&	&	\\
		$E$		&	2	&	-1	&	2	&	0	&	0	&	&	($2z^2-x^2-y^2$, $x^2-y^2$)\\
		$T_1$	&	3	&	0	&	-1	&	1	&	-1	&	($R_x$, $R_y$, $R_z$)	&	\\
		$T_2$	&	3	&	0	&	-1	&	-1	&	1	&	($x$, $y$, $z$)	&	($xy$, $xz$, $yz$)	\\ \hline
	\end{tabular}
	\end{center}
	
	\end{enumerate}
		
	\end{solution}

\end{document}